\documentclass[]{letter}


\begin{document}
	% If you want headings on subsequent pages,
	% remove the ``%'' on the next line:
	% \pagestyle{headings}
	
	\begin{letter}{ Ericsson - Ottawa Center\\
			349 Terry Fox Drive \\	
			Ottawa, Ontario, Canada \\
			K2K 2V6}
		\address{Nghia Doan\\ 3455 Rue Durocher, Apt\# 108 \\ Montreal, QC, Canada\\ H2X 2C9 \\ Email: nghia.doan@mail.mcgill.ca \\ Phone: +1 514-776-5591}
		
		\opening{To Whom It May Concern:}
		
		I am writing to apply for the 5G Baseband Systems Developer position advertised in the Ericsson Careers website.
		
		The role appears to be a good fit for me, and I believe that my strong technical experience and education make me a competitive candidate for this position. My key strengths that would support my success in this position include:
		
		\begin{itemize}
			\item Strong background in digital communication systems with a focus on forward error-correction codes used in the 5G Physical Layer.
			\item Experience in applying ML algorithms to aid channel decoding algorithms.
			\item Good programming and problem solving skills.
			\item Highly self motivated and can work under high pressure.
		\end{itemize}
		
		Please see my resume for additional information on my experience.
		
		I can be reached anytime via email at nghia.doan@mail.mcgill.ca or by cell phone, (+1) 514-776-5591.
		
		Thank you for your time and consideration. I look forward to speaking with you about this employment opportunity.
		
		\vspace*{30pt}
		Sincerely,	
		
		Nghia Doan
		\signature{Nghia Doan}
		
%		\closing{}
		
		%enclosure listing
		%\encl{}
		
	\end{letter}
\end{document}
